\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-24 OaklandSubmission/ld.tex
comment on the security theorem

\nc{Super high level security theorem}
\subsubsection*{Security theorem} The protocols we generate provide simulation-based security against a semi-honest adversary, in the framework of ~\cite{gmw,can00,can01}. At a very high level, in this framework, parties are modeled as non-uniform interactive turing machines (ITMs), with inputs provided by an environment $\env$. An adversary $\adv$, selects and ``corrupts'' one of the parties - however, $\adv$ still follows the protocol specification. $\adv$ interacts with the $\env$, which observes the view of the corrupted party. At the end of the interaction, $\env$ outputs a single bit. Two different interactions are defined: the {\em real world} and an {\em ideal world}. In the real interaction, the parties run the protocol $\prot$ in the presence of $\adv$ and $\env$. Let $\real_{\prot,\adv,\env}$ denote the binary distribution ensemble describing $\env$'s output in this interaction. In the ideal interaction, parties send their inputs to an additional entity, a trusted functionality machine $\F$ that carries the desired computation truthfully. Let $\simu$ (the simulator) denote the adversary in this idealized execution, and $\ideal_{\F,\simu,\env}$ the binary distribution ensemble describing $\env$'s output after interacting with adversary $\simu$ and ideal functionality $\F$. A protocol $\prot$ is said to {\em securely realize} a functionality $\F$ if for every adversary $\adv$ in the real interaction, there is an adversary $\simu$ in the ideal interaction, such that no environment $\env$, on any input, can tell the real interaction apart from the ideal interaction, except with negligible probability (in the security parameter $\secparam$). More precisely, if the two binary distribution ensembles above are computationally indistinguishable.
\nc{I'm not happy with the theorem statement.}
\begin{theorem}[Security]\label{theorem:security}
Let $\F$ be a functionality in our source language with outputs (or observations) $O_1$, that is compiled into a protocol $\prot$ in our target language with outputs $O_2$, then $\prot$ securely realizes $\F$.  
\end{theorem}
\nc{We should probably connect things to earlier? Theorem 1 and 2 have very different languages.}
\noindent {\em Proof.} From Theorem \ref{theorem:correctness}, we have that the observations in $\prot$ and $\F$ are the same (i.e. $O_2 = O_1$). Now, from the simulation security of our backend (\cite{aby}), the proof of the above theorem follows. \nc{I dont know how to say more.}
  %% \\
  %% \[
  %% \begin{array}{rrcl}
  %%   \ftext{Value} & v &::=& c \mid [\overline{c_{i}}]_{n}\\
  %%   \ftext{Observation} & O &::=& \cdot \mid c; O\\
  %% \end{array}
  %% \]

>>>>

\nc{Super high level security theorem}
\subsubsection*{Security theorem} The protocols we generate provide
simulation-based security against a semi-honest adversary, in the
framework of ~\cite{gmw,can00,can01}. At a very high level, in this
framework, parties are modeled as non-uniform interactive turing
machines (ITMs), with inputs provided by an environment $\env$. An
adversary $\adv$, selects and ``corrupts'' one of the parties -
however, $\adv$ still follows the protocol specification. $\adv$
interacts with the $\env$, which observes the view of the corrupted
party. At the end of the interaction, $\env$ outputs a single bit. Two
different interactions are defined: the {\em real world} and an {\em
  ideal world}. In the real interaction, the parties run the protocol
$\prot$ in the presence of $\adv$ and $\env$. Let
$\real_{\prot,\adv,\env}$ denote the binary distribution ensemble
describing $\env$'s output in this interaction. In the ideal
interaction, parties send their inputs to an additional entity, a
trusted functionality machine $\F$ that carries the desired
computation truthfully. Let $\simu$ (the simulator) denote the
adversary in this idealized execution, and $\ideal_{\F,\simu,\env}$
the binary distribution ensemble describing $\env$'s output after
interacting with adversary $\simu$ and ideal functionality $\F$. A
protocol $\prot$ is said to {\em securely realize} a functionality
$\F$ if for every adversary $\adv$ in the real interaction, there is
an adversary $\simu$ in the ideal interaction, such that no
environment $\env$, on any input, can tell the real interaction apart
from the ideal interaction, except with negligible probability (in the
security parameter $\secparam$). More precisely, if the two binary
distribution ensembles above are computationally indistinguishable.
\nc{I'm not happy with the theorem statement.}
\begin{theorem}[Security]\label{theorem:security}
Let $\F$ be a functionality in our source language with outputs (or observations) $O_1$, that is compiled into a protocol $\prot$ in our target language with outputs $O_2$, then $\prot$ securely realizes $\F$.  
\end{theorem}
\nc{We should probably connect things to earlier? Theorem 1 and 2 have very different languages.}
\noindent {\em Proof.} From Theorem \ref{theorem:correctness}, we have
that the observations in $\prot$ and $\F$ are the same (i.e. $O_2 =
O_1$). Now, from the simulation security of our backend (\cite{aby}),
the proof of the above theorem follows. \nc{I dont know how to say
  more.}

\aseem{Can we give a construction of the simulator S in the ideal
  semantics? The simulator S whenever it receives an observable event,
  outputs it to Z, and whenever A receives a string in the real
  semantics, S outputs a random string to Z. Now, with theorem 1,
  observable events are same in the ideal and real semantics, and with
  the security of the crypto backend, the random strings and the
  strings in the protocol are indistinguishable. Is it
  incorrect/naive?

  Also, we should emaphasize here that the ideal semantics is the
  source semantics from Figure x and the real semantics is the circuit
  semantics from Figure y. For the target language semantics, we
  should emphasize that it does not have access to the secrets, so
  there are no observations there.
}

  %% \\
  %% \[
  %% \begin{array}{rrcl}
  %%   \ftext{Value} & v &::=& c \mid [\overline{c_{i}}]_{n}\\
  %%   \ftext{Observation} & O &::=& \cdot \mid c; O\\
  %% \end{array}
  %% \]
